%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{janus-resume}  
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[danish]{babel}
\usepackage{fontawesome5}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

\namesection{Janus Bo Andersen}{}{ % Your name
%\urlstyle{same}\url{http://debarghyadas.com} 
% Your website, LinkedIn profile or other web address
\faPhoneSquare* +65 97243507 (Singapore) | 
\href{mailto:janus@janusboandersen.dk}{\faEnvelope} | 
\href{https://github.com/janusboandersen}{\faGithub} | 
\href{https://www.linkedin.com/in/janusboandersen/}{\faLinkedin} | 
\href{https://jobbank.au.dk/profiles/janusboandersen}{AU Job Bank}

} 


%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.49\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\descript{Embedded systems engineering (electronics)}
\location{5th sem. (2018 – 2021) | Aarhus University}
Top of the year with current GPA 11.9 (12-point scale).
\vspace{\topsep}
\begin{tightitemize}
\item Software engineering and development of embedded, distributed and realtime systems on MCU, FPGA, SoC and Cloud platforms. \\
\item Experienced in RTOS, Linux systems prog., network and IOT tech. and DevOps tools. \\
\item Experienced in implementing DSP, algorithms, machine learning, etc. \\
\item Larger projects in web dev., robotics, dynamic systems and control, RFID, analog electronics, etc. \\
\item Project management and agile methods.
\item Active in the Education Committee.
\end{tightitemize}

\sectionspace % Some whitespace after the section

\descript{M.Sc. Finance (cand.merc.)}
\location{2009 | Aarhus University}
Top of the year with GPA 11.5 (12-point scale).
%\vspace{\topsep}
\begin{tightitemize}
\item Master's thesis: Commercialization of Microfinance. \\
\item Focus on corporate finance, financial engineering og quantitative methods. \\
\item Doing Business in China case competition with BCG and Novozymes. \\
\end{tightitemize}

\sectionspace % Some whitespace after the section

\descript{B.Sc. Economics and Business (HA)}
\location{2007 | Aarhus University}
Highest GPA of the year of 10.6 (old scale).
\begin{tightitemize}
\item Bachelor's thesis: Interest term structure models. \\
\item McKinsey Award and Scholarship 2007 (first prize for best result of the B.Sc. education). \\
\item Exchange at Singapore Management University. \\
\end{tightitemize}

\sectionspace % Some whitespace after the section

% \descript{Øvrigt} 
% \location{Case competitions, awards}
% Doing Business in China 2009, Boston Consulting Group og Novozymes. \\
% McKinsey Award og Legat 2007, førstepræmie for årgangens bedste resultat på bacheloruddannelsen. \\
% \sectionspace % Some whitespace after the section

%------------------------------------------------

%\descript{Matematisk student}
% \location{2002 | Viby Gymnasium}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Technical skills}

%\subsection{Programmering}

\location{Software: Languages, build and test systems}
C, C++11/14/17, Python 3, VBA, Ruby 2.x, shell 
\textbullet{} CMake 3.x 
\textbullet{} GoogleTest, Catch2 (C++), unittest (Py) \\
\sectionspace % Some whitespace after the section

\location{FPGA, SoC: Languages, build and test systems}
VHDL 
\textbullet{} Xilinx Vivado, SDK and Vitis
\textbullet{} ILA \\
\sectionspace % Some whitespace after the section

\location{Linux, Cloud, DevOps, Data bases, Web}
Oracle Linux 7, CentOS 7, Ubuntu 18.04, 20.04
\textbullet{} AWS
\textbullet{} Docker, compose
\textbullet{} Git, Github
\textbullet{} PostgreSQL, MongoDB
\textbullet{} Django and Flask (Py), Nginx, HTML5/CSS/Bootstrap 4
\sectionspace % Some whitespace after the section

\location{Data, analysis, visualization, DSP, etc.}
Matlab Toolboxes: Symbolic Math, Filter Design, DSP, Image Processing, Control System
\textbullet{} Python: NumPy, SciPy, Pandas, Scikit-learn, Matplotlib, Seaborn
\textbullet{} SAS: BASE, STAT and IML
\textbullet{} SAP: FI/CO and BW
\sectionspace % Some whitespace after the section

\location{Embedded hardware platforms}
Freescale (Arm Cortex-M0+), Beagle (Cortex-A8)
\textbullet{} Xilinx Zynq-7000 SoC (Cortex-A9 and Artix-7)
\textbullet{} TI C5535 \\
\sectionspace % Some whitespace after the section


%\subsection{Øvrige IT-værktøjer}
%MS Office \textbullet{} LaTeX \textbullet{} SAP FI/CO og BW \\
%\sectionspace % Some whitespace after the section
%\sectionspace % Some whitespace after the section

%\subsection{Sprog}
\location{Languages}
\inlinefocus{Danish} native,
\inlinefocus{English} fluent,
\inlinefocus{German} proficient (B2/C1),
\inlinefocus{Mandarin} basic.

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

%\section{Links} 

%LinkedIn \href{https://www.linkedin.com/in/janusboandersen}{\bf janusboandersen} \\

%\sectionspace % Some whitespace after the section


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.49\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Selected work experience}

\runsubsection{Novo Nordisk Philippines}
\descript{| Head of Finance, Legal, Logistics \& IT}

\location{2014 – 2016 | Manila, Philippines}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Turn-around in affiliate with new management team, market launch of new pharmaceutical products.
\item Leadership of department with 10 employees, focus on employee performance and development.
\item As responsible for budgets and finances, ensured that ambitious growth targets for sales and profits were reached two years in a row.
\item Drove improvement projects in planning, accounting, reporting and logistics processes.
\item Significant step-up in professionalism of operations and employee conditions as well as implementation of business ethics program. 
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Novo Nordisk A/S}
\descript{| Financial Risk Manager}

\location{2011 – 2014 | Corporate Treasury, Bagsværd}
\begin{tightitemize}
\item Driving capital structure mgmt. through recommendations to executive management and board of directors, and subsequent implementation.
\item Currency hedging; strategy and execution in re. to company exposure and mandate from board.
\item Responsible for project to implement a quantitative currency hedging and risk management model in cooperation with McKinsey and PwC. 
\item Communication of analyses of political and market developments.
\item Daily leadership of department graduate.
\item Liaising with core banks for operations and tenders.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Novo Nordisk A/S}
\descript{| Global Finance Grad.}

\location{2009-2011 | Denmark, India, China}
\begin{tightitemize}
\item The Graduate Program is a 2-year international talent program with rotations in four areas of Novo Nordisk's global finance org.
\item Project mgmt. within ``internal management consulting''. Finance Projects, Denmark.
\item Controlling and reporting, and distributor mgmt. Beijing, China.
\item Off-shoring of financial processes from HQ and affiliates, change management. Bangalore, India.
\item Measurement and reporting of enterprise risks in re. budgetary and strategic goals. Novo Nordisk Risk Office, Corporate Financial Planning, Denmark.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Jyske Bank A/S}
\descript{| Assist. Quant. Analyst}
\location{2007-2009 | Quantitative Research, Silkeborg}
\begin{tightitemize}
\item Implementation and testing of credit risk models on bank's loan portfolio.
\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{Aarhus Uni.}
\descript{| Instructor, Corp. Finance }
\location{2007-2008 | School of Business}

\sectionspace % Some whitespace after the section

\runsubsection{TDC A/S}
\descript{| Assist. Analyst}
\location{2004-2006 | TDC Business, Aarhus}


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}